Use Of Jigsaw Puzzle Solving Algorithms In The Real World

### 2023-11-25 LaTeX_paper/paper.tex
unify the content section

@@

\subsection{The Dataset}
The last step of the introduction is defining our
testing dataset. We need both digital and real world
puzzles to solve. The dataset used, as well as
the code, can be seen in the public GitHub
repository:~\url{https://github.com/lucaSartore/PuzzleSolver}.

\subsubsection{The Real-World Puzzle}
The first step involves selecting a real-world
puzzle for solving. It has been decided to utilize a
classic 1000-piece puzzle measuring 66cm x 50cm.
A printer's scanner is employed to digitize the individual pieces.

The puzzle has been scanned in various sub-sizes to facilitate the testing of different configurations.
A resolution of 1200 pixels per inch (ppi) has been employed to ensure a sharp and precise
depiction of the pieces, as seen in image~\cref{fig:figure_measurement_error}.
The puzzle has been scanned backward, using a black background.

@@

\subsubsection{The Digital Puzzle}

@@

\subsection{Splitting The Pieces}

@@

\subsection{Splitting The Sides}

@@

\subsection{Comparing The Sides}\label{document:my_comparator}
The last step in the setup, is to compare the sides that have been
generated before.
In order to generate a compatibility shore,
the program compute the following steps:

@@

@@

\section{The Solver}\label{document:my_solver}
The Solver that has been developed is not the primary focus of this
paper and cannot be considered state-of-the-art when compared
to the current best digital puzzle solvers. However, it may be
considered as such when compared to existing ``real-world'' puzzle solvers.

\subsection{Overview}
The algorithm itself is relatively straightforward.
It operates as a recursive procedure, initiating by recognizing all 2x2
sets of matching pieces through the combination of four individual pieces.
Subsequently, it extends this process to identify all 4x4 sets of matching pieces
by aggregating four 2x2 pieces, and this pattern continues recursively.

\subsection{Basic Components}
To implement the algorithm two fundamental object are defined
\begin{itemize}
  \item SinglePiece: which contains information about a single puzzle piece.
  \item PieceGroup\(<\)T\(>\) where T can be either a PieceGroup or a SinglePiece\newline
  This element encompasses four elements of type T, each with its own position (top right, top left, bottom left, bottom right).
\end{itemize}
Both SinglePiece and PieceGroup have an ``orientation'' attribute that goes from 0 to 3~\cref{fig:orientation}.
\begin{figure}[H]
  \caption{orientation attribute of an object}\label{fig:orientation}
  \centering
  \includegraphics[height=0.3\textwidth]{pictures/orientation.png}
\end{figure}

\subsubsection{The Levels}

\subsubsection{The Behaviors}

\subsubsection{Combining four objects}\label{document:combining_four_objects}

The process also checks that all individual pieces inside a newly
created object are different (because obviously is impossible to reuse the same piece twice to solve a puzzle)
\subsection{The Algorithm}

@@

\subsection{Setup}
We have tested many different sizes of real, and digital puzzles.
The real world puzzles have been obtained with a printer’s scanner, more data are available in REF SETUP.
The digital puzzles have been obtained from \url{https://puzzle.telegnom.org/}.
This web app can generate a puzzle from a dimension and a jitter value. The jitter is a parameter that controls
how unique and distorted the puzzle images are, see \cref{fig:jiiter}.
The default jitter used in the tests is 5\%.

>>>>

% To have a paragraph look like a subsubsubsection
\usepackage{titlesec}

\setcounter{secnumdepth}{4}

\titleformat{\paragraph}
{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
\titlespacing*{\paragraph}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}

@@

\subsection{The Dataset}
The last step of the introduction is defining our
testing dataset. We need both digital and real world
puzzles to solve. The dataset used, as well as
the code, can be seen in the public GitHub
repository:~\url{https://github.com/lucaSartore/PuzzleSolver}.
\label{document:dataset}
\subsubsection{The Real-World Puzzle}
The first step involves selecting a real-world
puzzle to solve. It has been decided to utilize a
classic 1000-piece puzzle measuring 66cm x 50cm.
A printer's scanner is employed to digitize the individual pieces.

The puzzle has been scanned in various sub-sizes to facilitate the testing of different configurations.
A resolution of 1200 pixels per inch (ppi) has been employed to ensure a sharp and precise
depiction of the pieces, as seen in~\cref{fig:figure_measurement_error}.
The puzzle has been scanned backward, using a black background.

@@

\subsubsection{The Digital Puzzle}
The digital puzzles have been obtained from \url{https://puzzle.telegnom.org/}.
This web app can generate a puzzle from a dimension and a jitter value. The jitter is a parameter that controls
how unique and distorted the puzzle images are, see \cref{fig:jiiter}.
The default jitter used in the tests is 5\%.

@@

\subsection{Our Splitter}

\subsubsection{Splitting The Pieces}

@@

\subsubsection{Splitting The Sides}

@@

\subsection{Our Comparator}\label{document:my_comparator}
The last step in the setup, is to compare the sides that have been
generated before.
In order to generate a compatibility shore,
the program compute the following steps:

@@

\subsection{Our Solver}\label{document:my_solver}
The Solver that has been developed is not the primary focus of this
paper and cannot be considered state-of-the-art when compared
to the current best digital puzzle solvers. However, it may be
considered as such when compared to existing ``real-world'' puzzle solvers.

\subsubsection{Overview}
The algorithm itself is relatively straightforward.
It operates as a recursive procedure, initiating by recognizing all 2x2
sets of matching pieces through the combination of four individual pieces.
Subsequently, it extends this process to identify all 4x4 sets of matching pieces
by aggregating four 2x2 pieces, and this pattern continues recursively.

\subsubsection{Basic Components}
To implement the algorithm two fundamental object are defined
\begin{itemize}
  \item SinglePiece: which contains information about a single puzzle piece.
  \item PieceGroup\(<\)T\(>\) where T can be either a PieceGroup or a SinglePiece\newline
  This element encompasses four elements of type T, each with its own position (top right, top left, bottom left, bottom right).
\end{itemize}
Both SinglePiece and PieceGroup have an ``orientation'' attribute that goes from 0 to 3~\cref{fig:orientation}.
\begin{figure}[H]
  \caption{orientation attribute of an object}\label{fig:orientation}
  \centering
  \includegraphics[height=0.3\textwidth]{pictures/orientation.png}
\end{figure}

\paragraph{The Levels}

\paragraph{The Behaviors}

\paragraph{Combining four objects}\label{document:combining_four_objects}

The process also checks that all individual pieces inside a newly
created object are different (because obviously is impossible to reuse the same piece twice to solve a puzzle)
\subsubsection{The Algorithm}

@@

@@

\subsection{Setup}
See~\cref{document:dataset} for a detailed
description of the setup.
